Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex
done editing methodology

\subsection{Comprehension Questions}
Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions. These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly. Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants, which were 79\% of all incomplete or bad responses (n = 465).

@@

The main purposes of these questions were to, firstly, determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not and, secondly, to investigate what information would most upset users when shared. Additionally, there were 13 questions which did not follow the above format, lacking <data> to be shared and/or a <recipient>. Of these questions, 5 questions were to calibrate with existing privacy work for smartphones and the other 7  were exploratory questions. The calibration questions were modeled after a mobile user study conducted by Felt et. al \cite{Felt}, where we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception. The remaining exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants. An example of a regular question, a calibration question, and exploratory question, respectively, are below:

@@

@@

\subsection{Smartphone Scenarios}
Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone. These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt et. al's mobile user study \cite{Felt} for eliciting varying reactions from users. These questions were the basis for the five calibration wearables scenarios from the above section. Because we asked users questions differing only by the device in question, we are able to see how the change in device changes users' risk perception. Additionally, we compare our participants' perceptions of wearable device scenarios with existing perceptions of mobile device scenarios.

@@

\subsection{A Regression Model}
(REDO) Talk about the REGRESSION MODEL here. Say that the data type was x\% responsible, the data recepient y\% responsible, and the device type z\% responsible for how upset people seemed to be when they answered the questions.

>>>>

%%% I actually think it flows better without having a subsection here..

%\subsection{Question Format} 
%
%\subsubsection{Comprehension Questions} 
%Talk about format here. 
%
%\subsubsection{Wearables Scenarios} 
%Talk about format here. 
%
%\subsubsection{Smartphone Scenarios} 
%Talk about format here. 
%
%\subsubsection{Risk and Benefit Assessment} 
%Talk about format here.

\subsection{Comprehension Questions}
Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions. These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly. Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants.

@@

The main purposes of these questions were to, firstly, determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not and, secondly, to investigate what information would most upset users when shared. Additionally, there were 13 questions which did not follow the above format, lacking <data> to be shared and/or a <recipient>.  The 13 exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants. An example of a regular question, a calibration question, and exploratory question, respectively, are below:

@@

\subsection{Smartphone Scenarios}
Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone. Unlike the wearables scenario questions, these questions only ask about various situations which may occur using a smartphone, without a <data> or <recipient>. These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt et. al's mobile user study \cite{Felt} for eliciting varying reactions from users.

@@

These questions were the basis for the five calibration wearables scenarios from the above section. Because we asked users questions differing only by the device in question, we are able to see how the change in device changes users' risk perception. Additionally, we compare our participants' perceptions of wearable device scenarios with existing perceptions of mobile device scenarios. Of the 13 exploratory questions in the wearables section, 5 of those questions were to calibrate with existing privacy work for smartphones and the other 7  were exploratory questions. These wearables questions, like the smart phone questions, were modeled after the mobile user study conducted by Felt et. al \cite{Felt}, but we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception.

@@
